Titeln på avhandlingens språk

### 2023-01-25 body/glossary.tex
impact results
more writing yay
duration
fixing papers
fixing paper and strucutre
restructuring

\newabbreviation{WCA}{WCA}{Wearable Cognitive Assistance}
\newabbreviation{AR}{AR}{Augmented Reality}
\newabbreviation{VR}{VR}{Virtual Reality}
\newabbreviation{XR}{XR}{eXtended Reality}
\newabbreviation{GPU}{GPU}{Graphical Processing Unit}
\newabbreviation{FPS}{FPS}{Frames Per Second}
\newabbreviation{DNN}{DNN}{Deep Neural Network}
\newabbreviation{CPS}{CPS}{Cyber-Physical System}
\newabbreviation{NCS}{NCS}{Networked Control System}
%\acroindefinite{NCS}{an}{a}

\newabbreviation{LAN}{LAN}{Local-Area Network}
\newabbreviation{WLAN}{WLAN}{Wireless Local-Area Network}
\newabbreviation{KPI}{KPI}{Key Performance Indicator}
\newabbreviation{WPAN}{WPAN}{Wireless Personal Area Network}
\newabbreviation{CSMA/CD}{CSMA/CD}{Carrier-Sense Multiple Access with Collision Detection}
\newabbreviation{OS}{OS}{Operating System}
\newabbreviation{UDP}{UDP}{User Datagram Protocol}
\newabbreviation{TCP}{TCP}{Transmission Control Protocol}
\newabbreviation{RMS}{RMS}{Root Mean Square}
\newabbreviation{RTT}{RTT}{Round-Trip Time}
\newabbreviation{CI}{CI}{Confidence Interval}
\newabbreviation{AP}{AP}{Access Point}
\newabbreviation{API}{API}{Application Programming Interface}
\newabbreviation{SSF}{SSF}{Swedish Foundation for Strategic Research}
\newabbreviation{TECoSA}{TECoSA}{Trustworthy Edge Computing Systems and Applications}
\newabbreviation{ABC}{ABC}{Abstract Base Class}

@@

\newabbreviation{URL}{URL}{Uniform Record Locator}
\newabbreviation{AWS}{AWS}{Amazon Web Services}
\newabbreviation{EC2}{EC2}{Elastic Compute 2}
\newabbreviation{AMI}{AMI}{Amazon Machine Image}
\newabbreviation{SSH}{SSH}{Secure Shell}
\newabbreviation{IP}{IP}{Internet Protocol}
\newabbreviation{VPN}{VPN}{Virtual Private Network}
\newabbreviation{NAT}{NAT}{Network Address Translation}
\newabbreviation{NTP}{NTP}{Network Time Protocol}

@@

\newabbreviation{SDR}{SDR}{Software-Defined Radio}

@@

\newabbreviation{VLAN}{VLAN}{Virtual Local-Area Network}
\newabbreviation{APT}{APT}{Advaced Packaging Tool}
\newabbreviation{LTE}{LTE}{Long-Term Evolution}
\newabbreviation{SSID}{SSID}{Service Set Identifier}
\newabbreviation{EPC}{EPC}{Evolved Packet Core}
\newabbreviation{UE}{UE}{User Equipment}
\newabbreviation{eNodeB}{eNodeB}{Evolved Node B}
\newabbreviation{DNS}{DNS}{Domain Name System}
\newabbreviation{MNIST}{MNIST}{Modified National Institute of Standards and Technology}
\newabbreviation{HTTP}{HTTP}{Hyper-Text Transfer Protocol}

@@

\newabbreviation{YAML}{YAML}{YAML Ain't Markup Language}
\newabbreviation{O-RAN}{O-RAN}{Open Radio Access Network}
\newabbreviation{FOSS}{FOSS}{Free and Open Source Software}
\newabbreviation{COSMOS}{COSMOS}{Cloud enhanced Open Software defined MObile wireless testbed for city-Scale deployment}
\newabbreviation{OMF}{OMF}{ORBIT Management Framework}
\newabbreviation{POWDER}{POWDER}{Platform for Open Wireless Data-driven Experimental Research}
\newabbreviation{COTS}{COTS}{Commercial Off-The-Shelves}
\newabbreviation{RF}{RF}{Radio-Frequency}
\newabbreviation{VM}{VM}{Virtual Machine}
\newabbreviation{REST}{REST}{REpresentational Sate Transfer}
\newabbreviation{MaaS}{MaaS}{Metal-as-a-Service}
\newabbreviation{OEDL}{OEDL}{\gls{OMF} Experiment Description Language}
\newabbreviation{RSpec}{RSpec}{Resource Specification}
\newabbreviation{LXC}{LXC}{LinuX Containers}
\newabbreviation{MEC}{MEC}{Mobile Edge Computing}
\newabbreviation{USRP}{USRP}{Universal Software Radio Peripheral}
\newabbreviation{OAI}{OAI}{OpenAirInterface}
\newabbreviation{NR}{NR}{New Radio}
\newabbreviation{FPGA}{FPGA}{Field-Programmable Gate Array}
\newabbreviation{ARA}{ARA}{Agricultural and ruRAl communities}
\newabbreviation{UHF}{UHF}{Ultra-High Frequency}
\newabbreviation{MIMO}{MIMO}{Multi-Input Multi-Output}
\newabbreviation{CHI}{CHI}{CHameleon Infrastructure}
\newabbreviation{CMU}{CMU}{Carnegie Mellon University}
\newabbreviation{GSR}{GSR}{Galvanic Skin Response}
\newabbreviation{EEG}{EEG}{electroencephalography}
\newabbreviation{BFI}{BFI}{Big Five Inventory of personality traits~\cite{john1999big}}
\newabbreviation{ITQ}{ITQ}{Immersive Tendencies Questionnaire~\cite{witmer1998measuring}}
\newabbreviation{GPS}{GPS}{Global Positioning System}
\newabbreviation{FSM}{FSM}{Finite State Machine}
%\acroindefinite{NCS}{an}{a}
\newabbreviation{CLEAVE}{CLEAVE}{ControL bEnchmArking serVice on the Edge}
\newabbreviation{TTF}{TTF}{Time-to-Feedback}
\newabbreviation{MAR}{MAR}{Mobile \gls{AR}}
\newabbreviation{QoE}{QoE}{Quality of Experience}
\newabbreviation{QoS}{QoS}{Quality of Service}
\newabbreviation{PCA}{PCA}{Principal Component Analysis}
\newabbreviation{exGaussian}{Ex-Gaussian}{Exponentially Modified Gaussian}
\newabbreviation{IEEE}{IEEE}{Institute of Electrical and Electronics Engineers}
\newabbreviation{CPU}{CPU}{Central Processing Unit}
\newabbreviation{N/A}{N/A}{Not Applicable}
\newabbreviation{CIO}{CIO}{Confidence Interval}
\newabbreviation{MLE}{MLE}{Maximum Likelihood Estimation}
\newabbreviation{CDF}{CDF}{Cumulative Distribution Function}
\newabbreviation{CCDF}{CCDF}{Complementary \gls{CDF}}
\newabbreviation{PDF}{PDF}{Probability Density Function}
\newabbreviation{ECDF}{ECDF}{Empirical \gls{CDF}}
\newabbreviation{NSF}{NSF}{United States National Science Foundation}

>>>>

%! suppress = MissingImport
\newacronym[longplural={Wearable Cognitive Assistants}]{WCA}{WCA}{Wearable Cognitive Assistance}
\newacronym[longplural={Augmented Realities}]{AR}{AR}{Augmented Reality}
\newacronym[longplural={Virtual Realities}]{VR}{VR}{Virtual Reality}
\newacronym[longplural={eXtended Realities}]{XR}{XR}{eXtended Reality}
\newacronym{GPU}{GPU}{Graphical Processing Unit}
\newacronym{FPS}{FPS}{Frames Per Second}
\newacronym{DNN}{DNN}{Deep Neural Network}
\newacronym{CPS}{CPS}{Cyber-Physical System}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{NCS}{NCS}{Networked Control System}
%\acroindefinite{NCS}{an}{a}

\newacronym{LAN}{LAN}{Local-Area Network}
\newacronym{WLAN}{WLAN}{Wireless Local-Area Network}
\newacronym{KPI}{KPI}{Key Performance Indicator}
\newacronym{WPAN}{WPAN}{Wireless Personal Area Network}
\newacronym{CSMA/CD}{CSMA/CD}{Carrier-Sense Multiple Access with Collision Detection}
\newacronym{OS}{OS}{Operating System}
\newacronym{UDP}{UDP}{User Datagram Protocol}
\newacronym{TCP}{TCP}{Transmission Control Protocol}
\newacronym{RMS}{RMS}{Root Mean Square}
\newacronym{RTT}{RTT}{Round-Trip Time}
\newacronym{CI}{CI}{Confidence Interval}
\newacronym{AP}{AP}{Access Point}
\newacronym{API}{API}{Application Programming Interface}
\newacronym[user1={Stiftelsen för Strategisk Forskning}]{SSF}{SSF}{Swedish Foundation for Strategic Research}
\newacronym{TECoSA}{TECoSA}{Trustworthy Edge Computing Systems and Applications}
\newacronym[longplural={Abstract Base Classes}]{ABC}{ABC}{Abstract Base Class}

@@

\newacronym{URL}{URL}{Uniform Record Locator}
\newacronym{AWS}{AWS}{Amazon Web Services}
\newacronym{EC2}{EC2}{Elastic Compute 2}
\newacronym{AMI}{AMI}{Amazon Machine Image}
\newacronym{SSH}{SSH}{Secure Shell}
\newacronym{IP}{IP}{Internet Protocol}
\newacronym{VPN}{VPN}{Virtual Private Network}
\newacronym{NAT}{NAT}{Network Address Translation}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{NTP}{NTP}{Network Time Protocol}

@@

\newacronym[prefixfirst={a\ }, prefix={an\ }]{SDR}{SDR}{Software-Defined Radio}

@@

\newacronym{VLAN}{VLAN}{Virtual Local-Area Network}
\newacronym{APT}{APT}{Advaced Packaging Tool}
\newacronym{LTE}{LTE}{Long-Term Evolution}
\newacronym{SSID}{SSID}{Service Set Identifier}
\newacronym{EPC}{EPC}{Evolved Packet Core}
\newacronym{UE}{UE}{User Equipment}
\newacronym{eNodeB}{eNodeB}{Evolved Node B}
\newacronym{DNS}{DNS}{Domain Name System}
\newacronym{MNIST}{MNIST}{Modified National Institute of Standards and Technology}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{HTTP}{HTTP}{Hyper-Text Transfer Protocol}

@@

\newacronym{YAML}{YAML}{YAML Ain't Markup Language}
\newacronym{O-RAN}{O-RAN}{Open Radio Access Network}
\newacronym{FOSS}{FOSS}{Free and Open Source Software}
\newacronym{COSMOS}{COSMOS}{Cloud enhanced Open Software defined MObile wireless testbed for city-Scale deployment}
\newacronym{OMF}{OMF}{ORBIT Management Framework}
\newacronym{POWDER}{POWDER}{Platform for Open Wireless Data-driven Experimental Research}
\newacronym{COTS}{COTS}{Commercial Off-The-Shelves}
\newacronym{RF}{RF}{Radio-Frequency}
\newacronym{VM}{VM}{Virtual Machine}
\newacronym{REST}{REST}{REpresentational Sate Transfer}
\newacronym{MaaS}{MaaS}{Metal-as-a-Service}
\newacronym{OEDL}{OEDL}{\glsfmtshort{OMF} Experiment Description Language}
\newacronym{RSpec}{RSpec}{Resource Specification}
\newacronym{LXC}{LXC}{LinuX Containers}
\newacronym{MEC}{MEC}{Mobile Edge Computing}
\newacronym{USRP}{USRP}{Universal Software Radio Peripheral}
\newacronym{OAI}{OAI}{OpenAirInterface}
\newacronym{NR}{NR}{New Radio}
\newacronym{FPGA}{FPGA}{Field-Programmable Gate Array}
\newacronym{ARA}{ARA}{Agricultural and ruRAl communities}
\newacronym{UHF}{UHF}{Ultra-High Frequency}
\newacronym{MIMO}{MIMO}{Multi-Input Multi-Output}
\newacronym{CHI}{CHI}{CHameleon Infrastructure}
\newacronym{CMU}{CMU}{Carnegie Mellon University}
\newacronym{GSR}{GSR}{Galvanic Skin Response}
\newacronym{EEG}{EEG}{ElectroEncephaloGraphy}
\newacronym{BFI}{BFI}{Big Five Inventory of personality traits}
\newacronym{ITQ}{ITQ}{Immersive Tendencies Questionnaire}
\newacronym{GPS}{GPS}{Global Positioning System}
\newacronym{FSM}{FSM}{Finite State Machine}
\newacronym{CLEAVE}{CLEAVE}{ControL bEnchmArking serVice on the Edge}
\newacronym[longplural={Times-to-Feedback}]{TTF}{TTF}{Time-to-Feedback}
\newacronym{MAR}{MAR}{Mobile \glsfmtshort{AR}}
\newacronym{QoE}{QoE}{Quality of Experience}
\newacronym{QoS}{QoS}{Quality of Service}
\newacronym{PCA}{PCA}{Principal Component Analysis}
\newacronym{exGaussian}{Ex-Gaussian}{Exponentially Modified Gaussian}
\newacronym{IEEE}{IEEE}{Institute of Electrical and Electronics Engineers}
\newacronym{CPU}{CPU}{Central Processing Unit}
\newacronym{N/A}{N/A}{Not Applicable}
\newacronym{CIO}{CIO}{Confidence Interval}
\newacronym{MLE}{MLE}{Maximum Likelihood Estimation}
\newacronym{CDF}{CDF}{Cumulative Distribution Function}
\newacronym{CCDF}{CCDF}{Complementary \glsfmtshort{CDF}}
\newacronym{PDF}{PDF}{Probability Density Function}
\newacronym{ECDF}{ECDF}{Empirical \glsfmtshort{CDF}}
\newacronym{NSF}{NSF}{United States National Science Foundation}
\newacronym{ANOVA}{ANOVA}{ANalysis Of VAriance}
\newacronym{CV}{CV}{Computer Vision}
\newacronym{SEM}{SEM}{Standard Error of the Mean}

\glsaddall%

### 2023-01-25 body/part1/overview/extending-wca.tex
restructuring

\section{Implications of the methodology in the context of \acs{WCA}}\label{sec:extendingmethodology}

@@

\begin{figure}
    \begin{minipage}[t]{.45\textwidth}
        \centering
        \includegraphics[height=13em]{Figs/2021Impact/previousblock_vs_exectime}
        \caption{Mean execution time of the first slice of steps in a block, grouped by \acs{TTF} of the block immediately preceding the current one.}\label{fig:prevblockvsexectime}
    \end{minipage}%
    \hfill%
    \begin{minipage}[t]{.45\textwidth}
        \centering
        \includegraphics[height=13em]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0}
        \caption{%
            Illustration of the effect of neuroticism on the \ensuremath{\mu} parameter of \acs{exGaussian} distributions fitted to the execution times of steps in slice \num{1}.
            Fits were achieved through \gls{MLE}.
        }\label{fig:ttfvsexgaussianmu}
    \end{minipage}
\end{figure}

@@

\subsection{A new model of human behavior in \acs{WCA}}

@@

\subsubsection{Procedural generation of dynamic traces of video frames for \acs{WCA}}\label{model:traces}

@@

The main question we aim to ask relates to the consequences of using our model of human timing behaviors versus using a less realistic approximation.
Specifically, we aim to quantify the difference in task completion times when using the realistic model compared to a baseline which does not take into consideration higher order effects on execution times.
In \cref{fig:taskcompletiontimesdiff} we present the results of an experimental exploration of this difference.
We compare the total task durations of emulated \num{45}-step tasks using the EdgeDroid benchmarking tool with the improved model of human behavior to a baseline model.
Our reference baseline corresponds here to a first order approximation to empirical execution time modeling, using an \gls{exGaussian} distribution fitted to \emph{all} the data points from \cref{paper:olguinmunoz2021impact} (without any grouping) which is randomly sampled to obtain execution time values.
We perform this experiment on the edge computing testbed discussed in \cref{sec:testbed};
for simplicity and to magnify the effects of latency, in this setup we use an \acs{IEEE} \num{802.11}b/g physical layer.

>>>>

\section{Implications of the methodology in the context of \glsfmtshort{WCA}}\label{sec:extendingmethodology}

@@

\begin{figure}
    \begin{minipage}[t]{.45\textwidth}
        \centering
        \includegraphics[height=13em]{Figs/2021Impact/previousblock_vs_exectime}
        \caption{Mean execution time of the first slice of steps in a block, grouped by \glsfmtshort{TTF} of the block immediately preceding the current one.}\label{fig:prevblockvsexectime}
    \end{minipage}%
    \hfill%
    \begin{minipage}[t]{.45\textwidth}
        \centering
        \includegraphics[height=13em]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0}
        \caption{%
            Illustration of the effect of neuroticism on the \ensuremath{\mu} parameter of \glsfmtshort{exGaussian} distributions fitted to the execution times of steps in slice \num{1}.
            Fits were achieved through \gls{MLE}.
        }\label{fig:ttfvsexgaussianmu}
    \end{minipage}
\end{figure}

@@

\subsection{A new model of human behavior in \glsfmtshort{WCA}}

@@

\subsubsection{Procedural generation of dynamic traces of video frames for \glsfmtshort{WCA}}\label{model:traces}

@@

The main question we aim to ask relates to the consequences of using our model of human timing behaviors versus using a less realistic approximation.
Specifically, we aim to quantify the difference in task completion times when using the realistic model compared to a baseline which does not take into consideration higher order effects on execution times.
In \cref{fig:taskcompletiontimesdiff} we present the results of an experimental exploration of this difference.
We compare the total task durations of emulated \num{45}-step tasks using the EdgeDroid benchmarking tool with the improved model of human behavior to a baseline model.
Our reference baseline corresponds here to a first order approximation to empirical execution time modeling, using an \gls{exGaussian} distribution fitted to \emph{all} the data points from \cref{paper:olguinmunoz2021impact} (without any grouping) which is randomly sampled to obtain execution time values.
We perform this experiment on the edge computing testbed discussed in \cref{sec:testbed};
for simplicity and to magnify the effects of latency, in this setup we use an \glsfmtshort{IEEE} \num{802.11}b/g physical layer.

### 2023-01-25 body/part1/overview/methodology.tex
restructuring

@@

%\subsection{Applying the methodology to \acs{WCA}}\label{ssec:methodology:wca}

@@

\todo[inline]{}

%\subsection{Applying the methodology to \acsp{NCS}}

\todo[inline]{}

\subsection{Construction of a testbed for the implementation of the methodology}\label{sec:testbed}

\todo[inline]{}

>>>>

\subsection{Use case: \glsfmtshort{WCA}}\glsreset{WCA}

\todo[inline]{Discuss, at high level, the advantages of this methodology for WCA.
Challenges, opportunities. Maybe refer to the ``use cases'' of the first edgedroid paper.}

\subsection{Use case: \glsfmtshortpl{NCS}}\glsreset{NCS}

\todo[inline]{Discuss, at high level, the advantages ofthis methodology for NCSs.
Refer back to related work. }

\subsection{Tools for the application of the methodology}

\todo[inline]{Here we actually present the tools}

\subsubsection{\glsfmtshort{WCA}: EdgeDroid}

\subsubsection{\glsfmtshortpl{NCS}: CLEAVE}

\subsubsection{Testbeds: Ainur}

\todo[inline]{%
Everything below is ``old'' stuff that needs to be re-edited.%
}

@@

%\subsection{Applying the methodology to \glsfmtshort{WCA}}\label{ssec:methodology:wca}

@@

### 2023-01-25 publications/2021ImpactDelayedResponse/body.tex
restructuring

\subsection{\acs{EEG}}
Analyses were conducted on the log \gls{EEG} power in the alpha band, beta band, and total of all bands measured.
Readings from the two frontally placed poles were highly correlated and were pooled into an average.
Logs were taken for analysis because the \gls{EEG} distribution tended to have a rightward tail.
Twelve participants were excluded from the analysis, 9 due to device failure and 3 because of extreme values (i.e., the participant mean of log total power was greater than 3 s.d.s.\ from the mean of all participants).

@@

\subsection{\acs{GSR} and Heart Rate}
The measure of \gls{GSR} was the log of total amplitude in the signal.
To control for effects of block length (steps~\( \times \)~delay) and the slow-down in execution time at longer delays, \gls{GSR} data were normalized by the temporal duration of the block.
Due to sensor failure and the elimination of one subject with extreme values of \gls{GSR} amplitude using the same rule as for \gls{EEG}, the analysis comprised 34 participants.
No systematic trend due to delay or block length was observed.
In addition, the same analysis of slice position within block length as was performed for the \gls{EEG} revealed no effects, indicating that \gls{GSR} was stable across step positions within a block.

>>>>

\subsection{\glsfmtshort{EEG}}
Analyses were conducted on the log \gls{EEG} power in the alpha band, beta band, and total of all bands measured.
Readings from the two frontally placed poles were highly correlated and were pooled into an average.
Logs were taken for analysis because the \gls{EEG} distribution tended to have a rightward tail.
Twelve participants were excluded from the analysis, 9 due to device failure and 3 because of extreme values (i.e., the participant mean of log total power was greater than 3 s.d.s.\ from the mean of all participants).

@@

\subsection{\glsfmtshort{GSR} and Heart Rate}
The measure of \gls{GSR} was the log of total amplitude in the signal.
To control for effects of block length (steps~\( \times \)~delay) and the slow-down in execution time at longer delays, \gls{GSR} data were normalized by the temporal duration of the block.
Due to sensor failure and the elimination of one subject with extreme values of \gls{GSR} amplitude using the same rule as for \gls{EEG}, the analysis comprised 34 participants.
No systematic trend due to delay or block length was observed.
In addition, the same analysis of slice position within block length as was performed for the \gls{EEG} revealed no effects, indicating that \gls{GSR} was stable across step positions within a block.
